Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Literally one sentence about Pret-a-Voter.
Don't use `multicol` package
It prevents us from using the standard `figure` environment.

I got the new technique for creating a one-column abstract from:
http://www.tex.ac.uk/cgi-bin/texfaq2html?label=onecolabs.
Include mixnet depiction in paper
Remove TODO regarding an unnecessary image
Correct image path
Include Prˆet `a Voter ballot image
Figure links should go to the top of the image
Fortunately, there was an easy fix:
https://en.wikibooks.org/wiki/LaTeX/Labels_and_Cross-referencing#Pictures.
Rework discussion of Helios mixnet and decryption ver

% setup
\documentclass[10pt]{article}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{microtype}

@@

% document
\begin{document}
\maketitle

\thispagestyle{empty}

\begin{abstract}

@@

\end{abstract}

\begin{multicols}{2}

@@

@@

The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
$N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext
$c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
the random input at encrypt time been different} by a particular amount $s_{i}$.

@@

Finally, votes are decrypted and tallied. At this time, Helios also publishes the information
necessary for anyone who wishes to audit the election to verify that the mixnet's shuffling and
decryption were performed properly.

In order to provide a guarantee of proper shuffling, Helios actually shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles are
referred to as ``shadow mixes'' and are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as an ``Honest-Verifier Zero-Knowledge'' proof, for which the probability that the final
product is correct is equal to $1 - 2^{t}$, where $t$ is the number of shadow mixes produced.

Similarly, the Chaum-Peterson zero-knowledge proof technique is used to prove that decryption is
correct. \todo{How much detail should we provide?}

@@

\todo{Include image showing difference between Scantegrity and Helios voting mappings.}

@@

\end{multicols}

>>>>

% setup
\documentclass[10pt,twocolumn]{article}
\usepackage{abstract}
\usepackage[hypcap]{caption}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}
\nonstopmode

@@

% document
\begin{document}
\thispagestyle{empty}

\twocolumn[
\maketitle
\begin{onecolabstract}

@@

\end{onecolabstract}
]

@@

\pv\ aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/preta.pdf}
	\caption{\pv{} ballot}
	\label{fig:preta}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
	\caption{Re-encryption \term{mixnet}}
	\label{fig:mixnet}
\end{figure}

The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
$N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext
$c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
the random input at encrypt time been different} by a particular amount $s_{i}$. See Figure
~\ref{fig:mixnet} for a visual depiction of this process.

@@

In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles are
referred to as ``shadow mixes'' and are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
obtain the set of challenges allows this process to be completed entirely within the Helios system
-- without human involvement -- for publication and auditor verification.

Once auditors are satisfied with the proofs, Helios decrypts and tallies the ballots. Similarly,
Helios proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
decrypted ballots are in fact correct plaintexts for the corresponding mixnet outputs. Challenges
are generated by the system using a technique similar to that employed to provide mixnet proofs.

At that point, the election is complete and can be verified completely by any interested party.

@@

@@
